---
title: "Covid19 Analysis"
author: "Numrah Alauddin"
date: "12/10/2021"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---
```{r}
#Library Defined

knitr::opts_chunk$set(error = TRUE)
library(Hmisc)
library(factoextra)
library(dplyr)
```


Comment:
library(Hmisc): it contains many functions useful for data analysis, high-level graphics,utility operations, functions for computing sample size 
library(factoextra): is used to extract and visualize the output of exploratory multivariate data analysis.
library(dplyr):The package contains a set of functions (or “verbs”) that perform common data manipulation operations such as filtering for rows, selecting specific columns, re-ordering rows, adding new columns and summarizing data.


```{r}
#File that have been called for the data

data <- read.csv("C:/Users/ARSALAN IQBAL/Downloads/COVID19_line_list_data.csv")
data <- select(data,-c(X.1:X.6))
data <- select(data,-c(X))
data_copied <- data
describe(data)
data_copied$death_dummy <- as.integer(data$death !=0)
data_copied <- select(data_copied,-c(2,9,10,11,12,13,18,19))
data_copied <- na.omit(data_copied)
summary(data_copied)
```


Comment:
Summary() function displays the data after cleaning it from the junk data i.e. N/A data or NaN data is omitted to increase the accuracy of data. Thus, increasing the efficiency of results.
All the statistical data is displayed in the last of summary. All columns that has integer values resulted in these statistical data. This data will further be used to conclude promising results.




```{r}
#Deaths of the patients

death_all = subset(data_copied,death_dummy == 1)
hist(death_all$age, col='maroon',main='Deaths of All Covid Effecties w.r.t Age',xlab="Age")
```


Comment:
Histogram above shows that counts of death increases with the increase of age. Thus, age factor imposes a great impact on death due to COVID virus. Therefore, we can construct a result that greater the age, greater will the chance of death due to virus.



```{r}
#Gender wise Deaths (Male)

men <- subset(data_copied, gender == "male")
mendeath <- subset(men,death_dummy == 1)
hist(mendeath$age, col='brown',main='Deaths of Male Covid Effecties w.r.t Age',xlab="Age")
```



Comment:
Histogram above shows that male counts of death increases with the increase of age. Thus, age factor imposes a great impact on death due to COVID virus. Therefore, we can construct a result that greater the age, greater will the chance of death due to virus.







```{R}
#Gender wise Deaths (Female)

women <- subset(data_copied, gender == "female")
womendeath <- subset(women,death_dummy == 1)
hist(womendeath$age, col='light blue',main='Deaths of Female Covid Effecties w.r.t Age',xlab="Age")
```



Comment:
Histogram above shows that counts of overall death increases with the increase of age. Thus, age factor imposes a great impact on death due to COVID virus. Therefore, we can construct a result that greater the age, greater will the chance of death due to virus.





```{R}
#Called Principle Component Analysis on our data

head(data_copied)
data_copiedpc <- data_copied[,c(7,8,9)]
pc.data <- princomp(data_copiedpc, cor = TRUE)
screeplot(pc.data,type="l", main="Screeplot for the Covid Data")
abline(1,0,col= 'red',lty=2)
```



Comment:
Screeplot here indicates the out of 3 principle components i.e. (i) age, (ii) visiting wuhan and (iii) from wuhan, data majorly shows deviation from the Age components. It shows that whole data majorly variates with the age variable.


```{r}
#Confusion matrix

table(data_copied$death_dummy)
mymodel=glm(death_dummy~visiting.Wuhan+from.Wuhan+age,family=binomial,data_copied)
print(mymodel)
pmymodel=predict(mymodel,data_copied)
tab=table(pmymodel>0.5,data_copied$death_dummy)

print(tab)
accuracy <- sum(diag(tab))/sum(tab)*100
print(accuracy)
```

comment: This matrix showes the accuracy of our data.
